Combining bottom up and top down approaches for Drug-Target-Interaction prediction

### 2019-12-09 presentations/2019-12-09/presentation.tex
Added latest version of presentation
UPdated presentation, running graphsage again 1

\section{A medium approach to DTI prediction}
\begin{frame}{How to bring both approaches together?}
	\begin{enumerate}
		\item For each drug, filter possible targets according to protein based measurement
		\item Bring those together with the interaction networks for the prediction
	\end{enumerate}
	\pause
	Two hypotheses to be tested:
	\begin{itemize}
		\item Interaction only network sufficient?
		\item Does filter method increase performance?
	\end{itemize}
\end{frame}

@@

\begin{frame}{First results}
	\begin{figure}
		\small
		\centering
		\begingroup
		\def\arraystretch{1.2}
		\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
			\hline
			Approach  & \multicolumn{2}{c}{Layers} & \multicolumn{3}{|c|}{Acceptor} & \multicolumn{3}{c|}{Donor} \\
			\cline{2-9}
			&Conv. & Others & Acc. & Prec. & Rec. & Acc. & Prec. & Rec. \\
			\hline
			CNN DPDB & 4 & 5 & 94.4 & 95.4 & 94.6 & 94.9 & 94.4 & 94.7 \\
			CNN DPDB & 4 & 7 & 93.5 & 93.3 & 94.5 & 94.0 & 94.0 & 93.3 \\
			CNN DPDB & 6 & 5 & 94.0 & 93.9 & 94.9 & 94.2 & 95.4 & 91.6 \\
			CNN DPDB & 6 & 5 & 94.4 & 97.0 & 93.8 & 95.2 & 96.5 & 93.7 \\
			CNN DPDB & 2 & 4 & 94.3 & 95.6 & 94.3 & 95.3 & 96.9 & 94.4 \\
			SpliceRover & 4 & 2 & 96.1 & 93.9 & 97.4 & 95.4 & 95.6 & 96.7 \\
			Splice2Deep & - & - & 95.2 &  -- & 94.9 & 95.6 & -- & 98.8\\

			\hline  
		\end{tabular}
		\endgroup
	\end{figure}
\end{frame}

>>>>

\section{A medium approach to DTI prediction}
\begin{frame}{How to bring both approaches together?}
	\begin{exampleblock}{Algorithm}
		\begin{enumerate}
			\item For each drug, filter possible targets according to protein based measurement
			\item Bring those together with the interaction networks for the prediction
		\end{enumerate}
	\end{exampleblock}
	\pause
	Two hypotheses to be tested:
	\begin{itemize}
		\item Interaction only network sufficient?
		\item Does filter method increase performance?
	\end{itemize}
\end{frame}

@@

\begin{frame}{First results}
	\begin{figure}
		\centering
		\begingroup

		\footnotesize
		\def\arraystretch{1.2}
		\begin{tabular}{|r|r|r|r|r|r|r|r|}
			\hline
			\multicolumn{4}{|c|}{Used data}&layer sizes&model&Acc&AUC\\
			%\hline
			PPI&DDI&SE&HMM&&&&\\
			\hline
			1&1&0&0&641&graphsage&88.97&66.20\\
			1&1&0&0&641&graphsage&80.28&70.51\\
			1&1&0&0&641&graphsage&87.44&67.80\\
			1&1&0&0&641&graphsage&86.46&68.39\\
			1&1&0&0&641&graphsage&88.84&66.62\\
			1&1&1&0&641&graphsage&93.34&62.42\\
			1&1&1&0&641&graphsage&73.20&62.53\\
			1&1&1&0&641&graphsage&93.27&64.81\\
			1&1&1&0&641&graphsage&74.28&59.18\\
			1&1&1&0&641&graphsage&72.40&63.93\\
			1&1&1&0&641&gcn&88.61&67.27\\
			1&1&1&0&641&gat&82.65&71.69\\
			1&1&1&0&641&hinsage&83.18&70.33\\
			1&1&1&0&641&ppnp&89.80&67.78\\
			1&1&1&0&641&appnp&84.35&71.82\\
			1&1&1&0&641&sgc&86.50&68.45\\
			1&1&1&0&641&gcn&59.84&50.10\\
			1&1&1&0&641&gcn&97.11&56.02\\
			1&1&1&0&641&gat&59.77&50.06\\
			1&1&1&0&641&gat&55.48&55.93\\
			1&1&1&0&641&hinsage&59.77&50.06\\
			1&1&1&0&641&hinsage&94.06&63.52\\
			1&1&1&0&641&ppnp&21.54&50.15\\
			1&1&1&0&641&ppnp&77.98&55.85\\
			1&1&1&0&641&appnp&40.71&50.13\\
			1&1&1&0&641&sgc&2.27&50.18\\
			\hline  
		\end{tabular}
		\endgroup
	\end{figure}
\end{frame}

\begin{frame}{Future Work}
	\begin{itemize}
		\item Prove improvement of generalization
		\item Test performance against recent approaches
		\item Tweak model properly
		\item If performance and generalization is good enough:
		\begin{itemize}
			\item Test some predicted interactions in vitro
			\item Use DTI for Side-effect-phenotype mapping
		\end{itemize}
	\end{itemize}
\end{frame}
